|

### 2019-07-16 inst/manuscript/manuscript.Rmd
Add more GO terms to Fig 3
Also increase heatmap splits from 5 to 7

# GO term bar plots
f3_y <- plot_go_bar(f3_y_go_table, c(1:4, 49,52:53,55, 77,79:81), f3_pal) + 
  annotate("text", x = 12, y = 65, label = "bold('DAY286 Y')", parse = TRUE) + 
  labs(fill = "GO domain") + 
  theme(legend.text = element_text(size = 10), 
        legend.title = element_text(size = 10))

f3_b <- plot_go_bar(f3_b_go_table, c(1:4, 69,71:73, 96:97, 100, 102), f3_pal) + 
  annotate("text", x = 12, y = 60, label = "bold('DAY286 B')", parse = TRUE)

f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:3,6, 27,29,33,40, 46,49,51:52), f3_pal) + 
  annotate("text", x = 12, y = 70, label = "bold('ATCC90028')", parse = TRUE)

f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4, 62,65:66,76, 86:89), f3_pal) + 
  annotate("text", x = 12, y = 70, label = "bold('ATCC10231')", parse = TRUE)
```

```{r figure3, fig.cap=f3_cap, fig.width=7.2, fig.height=5}
# draw figure 4
ggarrange(f3_y, f3_a9, 
          f3_a1, f3_b, 
          labels = NULL, 
          ncol = 2, 
          nrow = 2, 
          common.legend = TRUE, 
          legend = "bottom", 
          align = "hv")

@@

# plot heatmap
f5_htmp <- plot_heatmap(mt = f5_table_filt, 
                        plot = FALSE,
                        df = FALSE, 
                        data_type = "log2fc", 
                        clust_fun = "gower", 
                        split_type = "cutree", 
                        k = 5, 
                        cluster_split = FALSE, 
                        split_order = c(2, 5, 1, 4, 3), 
                        colour_lims = c(-4, 4),
                        column_labels = c("ATCC90028", "ATCC10231", 
                                          "DAY286 Y", "DAY286 B"), 
                        col_name_fontsize = 6, 
                        column_names_rot = 45, 
                        row_title_fontsize = 6, 
                        row_title_rot = 0, 
                        row_title = c("1", "2", "3", "4", "5"), 
                        heatmap_legend_param = f5_params)

@@

```{r figure5Table, include=FALSE}
#  list of proteins for heatmap table in order of appearance in heatmap
f5_clusters <- plot_heatmap(mt = f5_table_filt, 
                            plot = FALSE,
                            df = TRUE, 
                            data_type = "log2fc", 
                            clust_fun = "gower", 
                            split_type = "cutree", 
                            k = 5, 
                            cluster_split = FALSE) %>% 
  mutate(cluster = recode(cluster, 
                          "1" = 4, "2" = 1, "3" = 5, "4" = 2, "5" = 3)) %>% 
  arrange(cluster)

>>>>

# GO term bar plots
f3_y <- plot_go_bar(f3_y_go_table, c(1:4,6, 23,26:28,30, 42,44:46), f3_pal) + 
  annotate("text", x = 14, y = 65, label = "bold('DAY286 Y')", parse = TRUE) + 
  labs(fill = "GO domain") + 
  theme(legend.text = element_text(size = 10), 
        legend.title = element_text(size = 10))

f3_b <- plot_go_bar(f3_b_go_table, c(1:4,6, 54:57,67, 73:75,77), f3_pal) + 
  annotate("text", x = 14, y = 60, label = "bold('DAY286 B')", parse = TRUE)

f3_a9 <- plot_go_bar(f3_a9_go_table, c(1:5, 12,14,17,18,24, 26:29), f3_pal) + 
  annotate("text", x = 14, y = 70, label = "bold('ATCC90028')", parse = TRUE)

f3_a1 <- plot_go_bar(f3_a1_go_table, c(1:4,6, 31,33:35,45, 49:52), f3_pal) + 
  annotate("text", x = 14, y = 70, label = "bold('ATCC10231')", parse = TRUE)
```

```{r figure3, fig.cap=f3_cap, fig.width=7.2, fig.height=6}
# draw figure 3
ggarrange(f3_y, f3_a9, 
          f3_a1, f3_b, 
          labels = NULL, 
          ncol = 2, 
          nrow = 2, 
          common.legend = TRUE, 
          legend = "bottom", 
          align = "hv")

@@

# plot heatmap
f5_htmp <- plot_heatmap(mt = f5_table_filt, 
                        plot = TRUE,
                        df = FALSE, 
                        data_type = "log2fc", 
                        clust_fun = "gower", 
                        split_type = "cutree", 
                        k = 7, 
                        cluster_split = FALSE, 
                        split_order = c(4, 1, 6, 2, 3, 5, 7), 
                        colour_lims = c(-4, 4),
                        column_labels = c("ATCC90028", "ATCC10231", 
                                          "DAY286 Y", "DAY286 B"), 
                        col_name_fontsize = 6, 
                        column_names_rot = 45, 
                        row_title = c("1", "2", "3", "4", "5", "6", "7"), 
                        row_title_fontsize = 6, 
                        row_title_rot = 0, 
                        heatmap_legend_param = f5_params)

@@

```{r figure5Table, include=FALSE}
#  list of proteins for heatmap table in order of appearance in heatmap
f5_clusters <- plot_heatmap(mt = f5_table_filt, 
                            plot = FALSE,
                            df = TRUE, 
                            data_type = "log2fc", 
                            clust_fun = "gower", 
                            split_type = "cutree", 
                            k = 7, 
                            cluster_split = FALSE) %>% 
  mutate(cluster = recode(cluster, 
                          "4" = 1, "1" = 2, "6" = 3, "2" = 4, 
                          "3" = 5, "5" = 6, "7" = 7)) %>% 
  arrange(cluster)
